---
output: github_document
---

## Quantile regression average

NB: This is a transient package that will probably be merged into the
[stackr package](https://github.com/nikosbosse/stackr). 

## Installation

The stable version of the package can be installed using
```{r eval=FALSE}
install.packages("qrensemble", repos = "https://epiforecasts.r-universe.dev/")
```

The development version can be installed using `pak`
```{r eval=FALSE}
pak::pak("epiforecasts/qrensemble")
```

### calculate QRA

Create an ensemble for each location, and separately for cases and deaths, for the 24th of July 2021
```{r}
library("qrensemble")
library("scoringutils")
example_quantile |>
  as_forecast_quantile() |>
  qra(
    group = c("target_type", "location", "location_name"),
    target = c(target_end_date = "2021-07-24")
  )
```

## Contributors


<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

All contributions to this project are gratefully acknowledged using the [`allcontributors` package](https://github.com/ropensci/allcontributors) following the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

### Code


<a href="https://github.com/epiforecasts/qrensemble/commits?author=sbfnk">sbfnk</a>, 
<a href="https://github.com/epiforecasts/qrensemble/commits?author=seabbs">seabbs</a>



### Issues


<a href="https://github.com/epiforecasts/qrensemble/issues?q=is%3Aissue+commenter%3Anikosbosse">nikosbosse</a>


<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->

